---
title: "Visualization Literacy Analysis"
author: "Derek Harter, Shulan Lu"
date: "11/12/2025"
output: pdf_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, knitr, ez, psychReport, superb, plotrix, emmeans, afex, readxl,
               irr, cccrm, foreign, stringr, glmmTMB, car) 

knitr::opts_chunk$set(echo = TRUE, tidy = FALSE)
options(width = 90)
```

## Read in data files

Raw data is in the `../AccData` subdirectory in two excel spreadsheet
files per participant. The following code combines into single dataframe
of all data.

```{r, warning=F, message=F}

#grab files from google drive (only have to do this once)
# source("getFromGoogleDrive.R")

#get the first 6? characters of each data file
#get unique values of these
# this is list of subject ids

raw_file_names <- list.files("../AccData")
first_six <- substr(raw_file_names, 1, 6)
sub_ids <- unique(first_six)


# fast_RTs <- data.frame(ParticipantId = character(),
#                        TrialName = character(),
#                        type = character(),
#                        time = numeric()
# )

all_data <- NULL

for (i in 1:length(sub_ids)){
  
  if (grepl("~$", sub_ids[i], fixed = T)){
    next
  }
  
  temp_file1 <- read_xlsx(paste0("../AccData/", sub_ids[i], "_1.xlsx")) %>%
    slice(1:17) %>%
    select(-starts_with("Order")) %>%
    rename(correct = 8)
  
  temp_file2 <- read_xlsx(paste0("../AccData/", sub_ids[i], "_2.xlsx")) %>%
    slice(1:17) %>%
     select(-starts_with("Order")) %>%
    rename(correct = 8)
  
  new_temp <- temp_file1 %>%
    bind_cols(temp_file2$correct) %>%
    rename(Correct_1 = correct, Correct_2 = "...9") %>%
    mutate(AnswerRT = TimeToBeginInput - TimeToReadQuestion)


  all_data <- all_data %>%
    bind_rows(new_temp)
  
}

all_data <- all_data %>%
  rename(readRT = TimeToReadQuestion, totalRT = TimeToBeginInput)

#read in trialtype key (I created this from an early version of the previous paper)
trial_type_key <- read.csv("../trial_type_key.csv", stringsAsFactors = F)

all_data <- all_data %>%
  mutate(TrialType = trial_type_key$TrialType[match(TrialName, trial_type_key$TrialName)]) %>%
  mutate(TrialType = paste0("Type",TrialType))


# remove temporary dataframes to keep workspace cleaner as we go forward
rm(new_temp)
rm(temp_file1)
rm(temp_file2)
rm(trial_type_key)
```

## Basic checks

Just a sanity check of all the data. Summary of number of subjects in
each of the 3 condition types.

```{r}

#how many participants per condition
all_data %>%
  group_by(ParticipantId, Condition) %>%
  summarize(ntrials = n()) %>%
  group_by(Condition) %>%
  summarize(nsubs = n()) %>%
  summary()

#why is the balance so off?


```

## Remove outliers based on RT

Removing outliers, resulting in data frame named `all_data_no_outliers`.

1.  All trials where the `AnswerRT` is less than 2 seconds are removed
    first, which assumes these reactions were too fast so were done
    without an actual considered response.
2.  All trials where the `AnswerRT` is 3 standard deviations different
    from the mean are removed next.

Table shows summary of mean and standard deviation of answer RT by each
of the trial question types, as well as the 3 standard deviation upper
and lower bound of the reaction time.

Displayed histogram is a sanity check of the number of trials each
participant in all of the data have done. Most participants should do 16
trials. Less than that are from dropped data for outliers.

```{r}

#removing on trial-by-trial basis


#remove answerRTs below 2000ms first
all_data_remove <- all_data %>%
  filter(AnswerRT >= 2000)
dim(all_data)[1]
dim(all_data_remove)[1]
#drops 7 trials

# also remove AnswerRT that are more than 3 standard deviations away from
# the mean
all_data_no_outliers <- all_data_remove %>%
  group_by(TrialName) %>%
  filter((!(abs(AnswerRT - mean(AnswerRT)) > 3.0*sd(AnswerRT))))
dim(all_data_no_outliers)[1]
#drops 47 more trials


rt_data_summary <- all_data_no_outliers %>%
  group_by(TrialName) %>%
  summarize(meanAnswerRT = mean(AnswerRT, na.rm = T),
            sdAnswerRT = sd(AnswerRT, na.rm = T),
            LB = meanAnswerRT - 3*sdAnswerRT,
            UB = meanAnswerRT + 3*sdAnswerRT)
summary(rt_data_summary)
rm(rt_data_summary)


all_data_no_outliers %>%
  group_by(ParticipantId) %>%
  summarize(ntrials = n()) %>%
  with(hist(ntrials, breaks = 0:17))

rm(all_data_remove)
##maybe consider replacing outliers with means instead of removing them?

```

## Extract Only One Type of Chart

Create a dataframe from the data with no outliers that contains only
XChartQ1 through XChartQ4 trials for the following analysis.

We replace the `all_data_no_outliers` dataframe with one containing only
the selected TrialName question type here, so past this point we are
analyzing only this particular TrialName type.

We show the table again of the mean RT for this question type. The table
should match the one done with all of the data, but we should only have
the particular question trial name type now in the data.

We also again plot the histogram of the number of trials. Participants
should have seen 4 of each particular question type, but after removing
outliers some only have 3, 2 or 1 remaining.

```{r}
all_data_no_outliers <- all_data_no_outliers %>%
  filter(grepl("BarChartQ[0-9]", TrialName))

rt_data_summary <- all_data_no_outliers %>%
  group_by(TrialName) %>%
  summarize(meanAnswerRT = mean(AnswerRT, na.rm = T),
            sdAnswerRT = sd(AnswerRT, na.rm = T),
            LB = meanAnswerRT - 3*sdAnswerRT,
            UB = meanAnswerRT + 3*sdAnswerRT)
summary(rt_data_summary)
rm(rt_data_summary)


all_data_no_outliers %>%
  group_by(ParticipantId) %>%
  summarize(ntrials = n()) %>%
  with(hist(ntrials, breaks = 0:4))
```

```{r}
#compare answer times 

trial_type_means <- all_data_no_outliers %>%
  group_by(ParticipantId, Condition, TrialType) %>%
  summarize(mean_answerRT = mean(AnswerRT), n = n())

# first, make .csv files in wide format to double check in statview
answer_rt <- trial_type_means %>%
  select(ParticipantId, Condition, TrialType, mean_answerRT) %>%
  pivot_wider(names_from = TrialType, values_from = mean_answerRT)

# fill in na values with mean for type1, type2 and type3 RT
# the following is supposed to work, but we get NaN from calculation of mean here, not sure why...
#read_rt_type_wider_clean <- read_rt_type_wider %>% mutate(across(Type1, ~replace_na(., mean(., na.rm=TRUE))))
answer_rt <- answer_rt %>% replace_na(list(Type1 = mean(answer_rt$Type1, na.rm=TRUE)))
answer_rt <- answer_rt %>% replace_na(list(Type2 = mean(answer_rt$Type2, na.rm=TRUE)))
answer_rt <- answer_rt %>% replace_na(list(Type3 = mean(answer_rt$Type3, na.rm=TRUE)))


answer_rt_summary <- answer_rt %>%
  group_by(Condition) %>%
  summarize(meanType1 = mean(Type1, na.rm = T),
            meanType2 = mean(Type2, na.rm = T),
            meanType3 = mean(Type3, na.rm=T))
kable(answer_rt_summary)
rm(answer_rt_summary)

#rm(trial_type_means)
```


### Alternative Analysis using glmm TMB package

The following analysis is for the heterogenous group condition analysis.  See
[]().

The following determines if a more complex model is justified.

```{r}

model_glmm_hom = glmmTMB(mean_answerRT ~ Condition * TrialType + (1 | ParticipantId),
                            data=trial_type_means, family = Gamma(link="log"),
                            dispformula = ~ 1, REML = FALSE)
model_glmm_hetero = glmmTMB(mean_answerRT ~ Condition * TrialType + (1 | ParticipantId),
                            data=trial_type_means, family = Gamma(link="log"),
                            dispformula = ~ Condition, REML = FALSE)


anova(model_glmm_hom, model_glmm_hetero)
```

### Try overall effect reporting

```{r}
fixed_effects_anova <- Anova(model_glmm_hom, type="III")
kable(fixed_effects_anova)
#summary(fixed_effects_anova, level=0.95)
```

### EMM on Condition and Interaction

If the glmm analysis is not significant, just use the homogeneous model.  Otherwise report on the more
complex heterogeneous model?

```{r}
emm_main_condition <- emmeans(model_glmm_hom,
                           specs = ~ Condition,
                           type = "response")

condition_results <- pairs(emm_main_condition)


summary(condition_results, level=0.95)
confint(condition_results, level=0.95)
#kable(condition_results)
```



```{r}
emm_interaction <- emmeans(model_glmm_hom,
                           specs = ~ Condition * TrialType,
                           type = "response")

simple_effects_results <- pairs(emm_interaction, by = "TrialType")


summary(simple_effects_results, level=0.95)
confint(simple_effects_results, level=0.95)
#kable(simple_effects_results)
```

### EMM by VR, VR Monitor, VR Monitor Stereo

```{r}
emm_main_condition <- emmeans(model_glmm_hom, 
                              specs = ~ Condition, 
                              type = "response")
summary(emm_main_condition, level=0.95)
confint(emm_main_condition, level=0.95)
```



Try explicitly naming the coefficients to remove all ambuugity

```{r}
comparison_results <- contrast(
  emm_main_condition,
  method = list(
    VR_vs_Monitors_Collapsed = c('VR' = 1, 'VR Monitor' = -0.5, 'VR Monitor Stereo' = -0.5)
  )
)

summary(comparison_results, infer = TRUE)
confint(comparison_results, level = 0.95)
```



Try explicitly naming the coefficients to remove all ambuugity

```{r}
comparison_results <- contrast(
  emm_main_condition,
  method = list(
    VRMonitor_vs_others_collapsed = c('VR' = -0.5, 'VR Monitor' = 1, 'VR Monitor Stereo' = -0.5)
  )
)

summary(comparison_results, infer = TRUE)
confint(comparison_results, level = 0.95)
```
