---
title: "Visualization Literacy Analysis"
author: "Derek Harter, Shulan Lu"
date: "11/12/2025"
output: pdf_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, knitr, ez, psychReport, superb, plotrix, emmeans, afex, readxl,
               irr, cccrm, foreign, stringr, glmmTMB, car) 

knitr::opts_chunk$set(echo = TRUE, tidy = FALSE)
options(width = 90)
```

## Read in data files

Raw data is in the `../AccData` subdirectory in two excel spreadsheet
files per participant. The following code combines into single dataframe
of all data.

```{r, warning=F, message=F}

#grab files from google drive (only have to do this once)
# source("getFromGoogleDrive.R")

#get the first 6? characters of each data file
#get unique values of these
# this is list of subject ids

raw_file_names <- list.files("../AccData")
first_six <- substr(raw_file_names, 1, 6)
sub_ids <- unique(first_six)


# fast_RTs <- data.frame(ParticipantId = character(),
#                        TrialName = character(),
#                        type = character(),
#                        time = numeric()
# )

all_data <- NULL

for (i in 1:length(sub_ids)){
  
  if (grepl("~$", sub_ids[i], fixed = T)){
    next
  }
  
  temp_file1 <- read_xlsx(paste0("../AccData/", sub_ids[i], "_1.xlsx")) %>%
    slice(1:17) %>%
    select(-starts_with("Order")) %>%
    rename(correct = 8)
  
  temp_file2 <- read_xlsx(paste0("../AccData/", sub_ids[i], "_2.xlsx")) %>%
    slice(1:17) %>%
     select(-starts_with("Order")) %>%
    rename(correct = 8)
  
  new_temp <- temp_file1 %>%
    bind_cols(temp_file2$correct) %>%
    rename(Correct_1 = correct, Correct_2 = "...9") %>%
    mutate(AnswerRT = TimeToBeginInput - TimeToReadQuestion)


  all_data <- all_data %>%
    bind_rows(new_temp)
  
}

all_data <- all_data %>%
  rename(readRT = TimeToReadQuestion, totalRT = TimeToBeginInput)

#read in trialtype key (I created this from an early version of the previous paper)
trial_type_key <- read.csv("../trial_type_key.csv", stringsAsFactors = F)

all_data <- all_data %>%
  mutate(TrialType = trial_type_key$TrialType[match(TrialName, trial_type_key$TrialName)]) %>%
  mutate(TrialType = paste0("Type",TrialType))


# remove temporary dataframes to keep workspace cleaner as we go forward
rm(new_temp)
rm(temp_file1)
rm(temp_file2)
rm(trial_type_key)
```

## Basic checks

Just a sanity check of all the data. Summary of number of subjects in
each of the 3 condition types.

```{r}

#how many participants per condition
all_data %>%
  group_by(ParticipantId, Condition) %>%
  summarize(ntrials = n()) %>%
  group_by(Condition) %>%
  summarize(nsubs = n()) %>%
  kable()

#why is the balance so off?


```

## Remove outliers based on RT

Removing outliers, resulting in data frame named `all_data_no_outliers`.

1.  All trials where the `AnswerRT` is less than 2 seconds are removed
    first, which assumes these reactions were too fast so were done
    without an actual considered response.
2.  All trials where the `AnswerRT` is 3 standard deviations different
    from the mean are removed next.

Table shows summary of mean and standard deviation of answer RT by each
of the trial question types, as well as the 3 standard deviation upper
and lower bound of the reaction time.

Displayed histogram is a sanity check of the number of trials each
participant in all of the data have done. Most participants should do 16
trials. Less than that are from dropped data for outliers.

```{r}

#removing on trial-by-trial basis


#remove answerRTs below 2000ms first
all_data_remove <- all_data %>%
  filter(AnswerRT >= 2000)
dim(all_data)[1]
dim(all_data_remove)[1]
#drops 7 trials

# also remove AnswerRT that are more than 3 standard deviations away from
# the mean
all_data_no_outliers <- all_data_remove %>%
  group_by(TrialName) %>%
  filter((!(abs(AnswerRT - mean(AnswerRT)) > 3.0*sd(AnswerRT))))
dim(all_data_no_outliers)[1]
#drops 47 more trials


rt_data_summary <- all_data_no_outliers %>%
  group_by(TrialName) %>%
  summarize(meanAnswerRT = mean(AnswerRT, na.rm = T),
            sdAnswerRT = sd(AnswerRT, na.rm = T),
            LB = meanAnswerRT - 3*sdAnswerRT,
            UB = meanAnswerRT + 3*sdAnswerRT)
kable(rt_data_summary)
rm(rt_data_summary)


all_data_no_outliers %>%
  group_by(ParticipantId) %>%
  summarize(ntrials = n()) %>%
  with(hist(ntrials, breaks = 0:17))

rm(all_data_remove)
##maybe consider replacing outliers with means instead of removing them?

```

## Extract Only One Type of Chart

Create a dataframe from the data with no outliers that contains only
XChartQ1 through XChartQ4 trials for the following analysis.

We replace the `all_data_no_outliers` dataframe with one containing only
the selected TrialName question type here, so past this point we are
analyzing only this particular TrialName type.

We show the table again of the mean RT for this question type. The table
should match the one done with all of the data, but we should only have
the particular question trial name type now in the data.

We also again plot the histogram of the number of trials. Participants
should have seen 4 of each particular question type, but after removing
outliers some only have 3, 2 or 1 remaining.

```{r}
all_data_no_outliers <- all_data_no_outliers %>%
  filter(grepl("LineChartQ[0-9]", TrialName))

rt_data_summary <- all_data_no_outliers %>%
  group_by(TrialName) %>%
  summarize(meanAnswerRT = mean(AnswerRT, na.rm = T),
            sdAnswerRT = sd(AnswerRT, na.rm = T),
            LB = meanAnswerRT - 3*sdAnswerRT,
            UB = meanAnswerRT + 3*sdAnswerRT)
kable(rt_data_summary)
rm(rt_data_summary)


all_data_no_outliers %>%
  group_by(ParticipantId) %>%
  summarize(ntrials = n()) %>%
  with(hist(ntrials, breaks = 0:5))
```

## Compare Read RT

Compare the reading reaction times for the selected question type.

### Extract wide dataframe

In this cell we convert the data to a wide format, selection only
Condition, TrialType and the mean_readRT, and widening the TrialType
column.

We have also filled in na/missing values here as a final step here.
Maybe we should instead just change from removing outliers to replacing
with mean. Also the filling missing values code here should be easier to
do, needs to be fixed. But result should be that any na in the resulting
wide table is replaced with the mean for the particular Type.

```{r}
#compare read times (should be no differences of condition)

trial_type_means <- all_data_no_outliers %>%
  group_by(ParticipantId, Condition, TrialType) %>%
  summarize(mean_readRT = mean(readRT), n = n())

# first, make .csv files in wide format to double check in statview
read_rt <- trial_type_means %>%
  select(ParticipantId, Condition, TrialType, mean_readRT) %>%
  pivot_wider(names_from = TrialType,values_from = mean_readRT)

# fill in na values with mean for type1, type2 and type3 RT
# the following is supposed to work, but we get NaN from calculation of mean here, not sure why...
#read_rt_type_wider_clean <- read_rt_type_wider %>% mutate(across(Type1, ~replace_na(., mean(., na.rm=TRUE))))
read_rt <- read_rt %>% replace_na(list(Type1 = mean(read_rt$Type1, na.rm=TRUE)))
read_rt <- read_rt %>% replace_na(list(Type2 = mean(read_rt$Type2, na.rm=TRUE)))
read_rt <- read_rt %>% replace_na(list(Type3 = mean(read_rt$Type3, na.rm=TRUE)))


read_rt_summary <- read_rt %>%
  group_by(Condition) %>%
  summarize(meanType1 = mean(Type1, na.rm = T),
            meanType2 = mean(Type2, na.rm = T),
            meanType3 = mean(Type3, na.rm=T))
kable(read_rt_summary)
rm(read_rt_summary)

#rm(trial_type_means)
```

### Basic plots of main effect and wider format

Plot of read RT condition main effect, as well as wider format plot by
the trial types.

```{r}

#just condition main effect
readplot1 <- all_data_no_outliers %>% 
   group_by(ParticipantId, Condition) %>% 
   summarize(overallmean = mean(readRT)) %>% 
   group_by(Condition) %>% 
   summarize(overall_condition_mean = mean(overallmean), 
             se = std.error(overallmean), 
             n = n(), 
             CI = qt(0.975,df=n-1)*se) 

 ggplot(readplot1, aes(Condition, 
                       overall_condition_mean, 
                       group = 1, 
                       ymin = overall_condition_mean - CI, 
                       ymax = overall_condition_mean + CI)) + 
   theme_classic() +  
   geom_point(size = 4) + 
   geom_errorbar(width = .15, linewidth = 0.85) +  
   geom_line(linewidth = 0.85) + 
   labs(y = "Reading RTs (ms)", title = "Read RTs") 

rm(readplot1)

#make a little plot using wide format
superbPlot(read_rt,
    BSFactors   = "Condition", 
    WSFactors   = "QuestionType(3)", 
    variables   = c("Type1", "Type2", "Type3"),
    statistic   = "meanNArm",
    errorbar    = "CI",
    gamma       = 0.95,
    adjustments = list(
        purpose       = "difference"
    ),
    plotLayout = "line",
    factorOrder = c("Condition", "QuestionType")
) + 
theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
facet_wrap(vars(QuestionType))+
labs(y = "Reading RTs (ms)", title = "Read RTs")

```

### Correct wider plot heterogeneous variance

The message from the superbPlot may indicate that some of the groups'
variances are heterogeneous. We can try using the `tryon` purpose option
as suggested, read [Unequal variances, Welch test, Tryon adjustment, and
superb](https://dcousin3.github.io/superb/articles/Vignette7.html).

```{r}
# make the wide plot, use tryon for purpose as suggested because of group's heterogeneous variances
superbPlot(read_rt,
    BSFactors   = "Condition", 
    WSFactors   = "QuestionType(3)", 
    variables   = c("Type1", "Type2", "Type3"),
    statistic   = "meanNArm",
    errorbar    = "CI",
    gamma       = 0.95,
    adjustments = list(
        purpose       = "tryon"
    ),
    plotLayout = "line",
    factorOrder = c("Condition", "QuestionType")
) + 
theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
facet_wrap(vars(QuestionType))+
labs(y = "Reading RTs (ms)", title = "Read RTs")

```

### Perform anova and post-hoc tests

Finally perform anova on the read RT data and various posthoc tests.

```{r}

# need back into long format for following, but we will use out dataframe
# will filled in na/missing and make wide again here
read_rt_long <- read_rt %>%
     pivot_longer(Type1:Type3, names_to="TrialType", values_to = "mean_readRT")

read_rt_anova <- aov_ez(id = "ParticipantId",
                        dv = "mean_readRT",
                        data = read_rt_long,
                        within = "TrialType",
                        between = "Condition",
                        anova_table = list(es = "pes") #might want to double-check these
)

kable(nice(read_rt_anova))

#posthoc test for trial type
pairs(emmeans(read_rt_anova, "TrialType"), adjust = "Tukey")

#posthoc test for condition, still using Tukey
pairs(emmeans(read_rt_anova, "Condition"), adjust = "Tukey")

#posthoc test for condition, others seem to be scheffe, sidak, bonferroni, dunnettx, mvt, none
pairs(emmeans(read_rt_anova, "Condition"), adjust = "scheffe")

rm(read_rt_long)
rm(read_rt_anova)
```

### Alternative Analysis using glmm TMB package

The following analysis is for the heterogenous group condition analysis.  See
[]().

The following determines if a more complex model is justified.

```{r}

model_glmm_hom = glmmTMB(mean_readRT ~ Condition * TrialType + (1 | ParticipantId),
                            data=trial_type_means, family = Gamma(link="log"),
                            dispformula = ~ 1, REML = FALSE)
model_glmm_hetero = glmmTMB(mean_readRT ~ Condition * TrialType + (1 | ParticipantId),
                            data=trial_type_means, family = Gamma(link="log"),
                            dispformula = ~ Condition, REML = FALSE)


anova(model_glmm_hom, model_glmm_hetero)
```

### Try overall effect reporting

```{r}
fixed_effects_anova <- Anova(model_glmm_hom, type="III")
kable(fixed_effects_anova)
```

### EMM on Condition and Interaction

If the glmm analysis is not significant, just use the homogeneous model.  Otherwise report on the more
complex heterogeneous model?

```{r}
emm_main_condition <- emmeans(model_glmm_hom,
                           specs = ~ Condition,
                           type = "response")

condition_results <- pairs(emm_main_condition)


kable(condition_results)
```

```{r}
emm_interaction <- emmeans(model_glmm_hom,
                           specs = ~ Condition * TrialType,
                           type = "response")

simple_effects_results <- pairs(emm_interaction, by = "TrialType")


kable(simple_effects_results)
```


## Compare Answer RT

### Extract wide dataframe

Do all of the previous, but for the answer reaction times for the
selected question types.

We again create a dataframe in needed format of only the answer RT data,
filling in na/missing values in the data.

```{r}
#compare answer times 

trial_type_means <- all_data_no_outliers %>%
  group_by(ParticipantId, Condition, TrialType) %>%
  summarize(mean_answerRT = mean(AnswerRT), n = n())

# first, make .csv files in wide format to double check in statview
answer_rt <- trial_type_means %>%
  select(ParticipantId, Condition, TrialType, mean_answerRT) %>%
  pivot_wider(names_from = TrialType, values_from = mean_answerRT)

# fill in na values with mean for type1, type2 and type3 RT
# the following is supposed to work, but we get NaN from calculation of mean here, not sure why...
#read_rt_type_wider_clean <- read_rt_type_wider %>% mutate(across(Type1, ~replace_na(., mean(., na.rm=TRUE))))
answer_rt <- answer_rt %>% replace_na(list(Type1 = mean(answer_rt$Type1, na.rm=TRUE)))
answer_rt <- answer_rt %>% replace_na(list(Type2 = mean(answer_rt$Type2, na.rm=TRUE)))
answer_rt <- answer_rt %>% replace_na(list(Type3 = mean(answer_rt$Type3, na.rm=TRUE)))


answer_rt_summary <- answer_rt %>%
  group_by(Condition) %>%
  summarize(meanType1 = mean(Type1, na.rm = T),
            meanType2 = mean(Type2, na.rm = T),
            meanType3 = mean(Type3, na.rm=T))
kable(answer_rt_summary)
rm(answer_rt_summary)

#rm(trial_type_means)
```

### Basic plots of main effect and wider format

Plot of answer RT condition main effect, as well as wider format plot by
the trial types.

```{r}

#just condition main effect
answerplot1 <- all_data_no_outliers %>% 
   group_by(ParticipantId, Condition) %>% 
   summarize(overallmean = mean(AnswerRT)) %>% 
   group_by(Condition) %>% 
   summarize(overall_condition_mean = mean(overallmean), 
             se = std.error(overallmean), 
             n = n(), 
             CI = qt(0.975,df=n-1)*se) 

 ggplot(answerplot1, aes(Condition, 
                       overall_condition_mean, 
                       group = 1, 
                       ymin = overall_condition_mean - CI, 
                       ymax = overall_condition_mean + CI)) + 
   theme_classic() +  
   geom_point(size = 4) + 
   geom_errorbar(width = .15, linewidth = 0.85) +  
   geom_line(linewidth = 0.85) + 
   labs(y = "Answer RTs (ms)", title = "Answer RTs") 

rm(answerplot1)

#make a little plot using wide format
superbPlot(answer_rt,
    BSFactors   = "Condition", 
    WSFactors   = "QuestionType(3)", 
    variables   = c("Type1", "Type2", "Type3"),
    statistic   = "meanNArm",
    errorbar    = "CI",
    gamma       = 0.95,
    adjustments = list(
        purpose       = "difference"
    ),
    plotLayout = "line",
    factorOrder = c("Condition", "QuestionType")
) + 
theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
facet_wrap(vars(QuestionType))+
labs(y = "Answer RTs (ms)", title = "Answer RTs")

```

### Correct wider plot heterogeneous variance

The message from the superbPlot may indicate that some of the groups'
variances are heterogeneous. We can try using the `tryon` purpose option
as suggested, read [Unequal variances, Welch test, Tryon adjustment, and
superb](https://dcousin3.github.io/superb/articles/Vignette7.html).

```{r}
# make the wide plot, use tryon for purpose as suggested because of group's heterogeneous variances
superbPlot(answer_rt,
    BSFactors   = "Condition", 
    WSFactors   = "QuestionType(3)", 
    variables   = c("Type1", "Type2", "Type3"),
    statistic   = "meanNArm",
    errorbar    = "CI",
    gamma       = 0.95,
    adjustments = list(
        purpose       = "tryon"
    ),
    plotLayout = "line",
    factorOrder = c("Condition", "QuestionType")
) + 
theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
facet_wrap(vars(QuestionType))+
labs(y = "Answer RTs (ms)", title = "Answer RTs")

```

### Perform anova and post-hoc tests

Finally perform anova on the answer RT data and various posthoc tests.

```{r}

# need back into long format for following, but we will use out dataframe
# will filled in na/missing and make wide again here
answer_rt_long <- answer_rt %>%
     pivot_longer(Type1:Type3, names_to="TrialType", values_to = "mean_answerRT")

answer_rt_anova <- aov_ez(id = "ParticipantId",
                          dv = "mean_answerRT",
                          data = answer_rt_long,
                          within = "TrialType",
                          between = "Condition",
                          anova_table = list(es = "pes") #might want to double-check these
)

kable(nice(answer_rt_anova))

#posthoc test for trial type
pairs(emmeans(answer_rt_anova, "TrialType"), adjust = "Tukey")

#posthoc test for condition, still using Tukey
pairs(emmeans(answer_rt_anova, "Condition"), adjust = "Tukey")

#posthoc test for condition, others seem to be scheffe, sidak, bonferroni, dunnettx, mvt, none
pairs(emmeans(answer_rt_anova, "Condition"), adjust = "scheffe")

rm(answer_rt_long)
rm(answer_rt_anova)
```

### Alternative Analysis using glmm TMB package

The following analysis is for the heterogenous group condition analysis.  See
[]().

The following determines if a more complex model is justified.

```{r}

model_glmm_hom = glmmTMB(mean_answerRT ~ Condition * TrialType + (1 | ParticipantId),
                            data=trial_type_means, family = Gamma(link="log"),
                            dispformula = ~ 1, REML = FALSE)
model_glmm_hetero = glmmTMB(mean_answerRT ~ Condition * TrialType + (1 | ParticipantId),
                            data=trial_type_means, family = Gamma(link="log"),
                            dispformula = ~ Condition, REML = FALSE)


anova(model_glmm_hom, model_glmm_hetero)
```

### Try overall effect reporting

```{r}
fixed_effects_anova <- Anova(model_glmm_hom, type="III")
kable(fixed_effects_anova)
```

### EMM on Condition and Interaction

If the glmm analysis is not significant, just use the homogeneous model.  Otherwise report on the more
complex heterogeneous model?

```{r}
emm_main_condition <- emmeans(model_glmm_hom,
                           specs = ~ Condition,
                           type = "response")

condition_results <- pairs(emm_main_condition)


kable(condition_results)
```

```{r}
emm_interaction <- emmeans(model_glmm_hom,
                           specs = ~ Condition * TrialType,
                           type = "response")

simple_effects_results <- pairs(emm_interaction, by = "TrialType")


kable(simple_effects_results)
```


## Compare Accuracy

### Extract wide dataframe

Do all of the previous again but on the Accuracy results.

We again create a dataframe in needed format of only the accuracy data.\
A bit different from before, only need to create an avverage of the two
correct features we have. But then we do a similar transformation into
wide format and replace na/missing values.

```{r}
all_data_no_outliers <- all_data_no_outliers %>%
  rowwise() %>%
  mutate(Correct_Avg = mean(c(Correct_1, Correct_2)))

trial_type_mean_accuracy <- all_data_no_outliers %>%
  group_by(ParticipantId, Condition, TrialType) %>%
  summarize(mean_acc = mean(Correct_Avg),
            n = n())

accuracy <- trial_type_mean_accuracy %>%
  select(ParticipantId, Condition, TrialType, mean_acc) %>%
  pivot_wider(names_from = TrialType, values_from = mean_acc)

# replace na with mean
accuracy <- accuracy %>% replace_na(list(Type1 = mean(accuracy$Type1, na.rm=TRUE)))
accuracy <- accuracy %>% replace_na(list(Type2 = mean(accuracy$Type2, na.rm=TRUE)))
accuracy <- accuracy %>% replace_na(list(Type3 = mean(accuracy$Type3, na.rm=TRUE)))

rm(trial_type_mean_accuracy)
```

### Basic plots of main effect and wider format

```{r}
#just condition main effect
accplot1 <- all_data_no_outliers %>% 
   group_by(ParticipantId, Condition) %>% 
   summarize(overallmean = mean(Correct_Avg)) %>% 
   group_by(Condition) %>% 
   summarize(overall_condition_mean = mean(overallmean), 
             se = std.error(overallmean), 
             n = n(), 
             CI = qt(0.975,df=n-1)*se) 

ggplot(accplot1, aes(Condition, 
                       overall_condition_mean, 
                       group = 1, 
                       ymin = overall_condition_mean - CI, 
                       ymax = overall_condition_mean + CI)) + 
   theme_classic() +  
   geom_point(size = 4) + 
   geom_errorbar(width = .15, linewidth = 0.85) +  
   geom_line(linewidth = 0.85) + 
   labs(y = "Accuracy", title = "Accuracy") 

rm(accplot1)

#make the little plot
superbPlot(accuracy,
    BSFactors   = "Condition", 
    WSFactors   = "QuestionType(3)", 
    variables   = c("Type1", "Type2", "Type3"),
    statistic   = "meanNArm",
    errorbar    = "CI",
    gamma       = 0.95,
    adjustments = list(
        purpose       = "difference"
    ),
    plotLayout = "line",
    factorOrder = c("Condition", "QuestionType")
) + 
theme_classic() + 
theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
facet_wrap(vars(QuestionType))+
labs(y = "Accuracy", title = "Accuracy") 
```

### Correct wider plot heterogeneous variance

The message from the superbPlot may indicate that some of the groups'
variances are heterogeneous. We can try using the `tryon` purpose option
as suggested, read [Unequal variances, Welch test, Tryon adjustment, and
superb](https://dcousin3.github.io/superb/articles/Vignette7.html).

```{r}
# make the wide plot, use tryon for purpose as suggested because of group's heterogeneous variances
superbPlot(accuracy,
    BSFactors   = "Condition", 
    WSFactors   = "QuestionType(3)", 
    variables   = c("Type1", "Type2", "Type3"),
    statistic   = "meanNArm",
    errorbar    = "CI",
    gamma       = 0.95,
    adjustments = list(
        purpose       = "tryon"
    ),
    plotLayout = "line",
    factorOrder = c("Condition", "QuestionType")
) + 
theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
facet_wrap(vars(QuestionType))+
labs(y = "Accuracy", title = "Accuracy")

```

### Perform anova and post-hoc tests

Finally perform anova on the accuracy data and various posthoc tests.

```{r}

# need back into long format for following, but we will use out dataframe
# will filled in na/missing and make wide again here
accuracy_long <- accuracy %>%
     pivot_longer(Type1:Type3, names_to="TrialType", values_to = "mean_acc")

accuracy_anova <- aov_ez(id = "ParticipantId",
                          dv = "mean_acc",
                          data = accuracy_long,
                          within = "TrialType",
                          between = "Condition",
                          anova_table = list(es = "pes") #might want to double-check these
)

kable(nice(accuracy_anova))

#posthoc test for trial type
pairs(emmeans(accuracy_anova, "TrialType"), adjust = "Tukey")

#posthoc test for condition, still using Tukey
pairs(emmeans(accuracy_anova, "Condition"), adjust = "Tukey")

#posthoc test for condition, others seem to be scheffe, sidak, bonferroni, dunnettx, mvt, none
pairs(emmeans(accuracy_anova, "Condition"), adjust = "scheffe")

rm(accuracy_long)
rm(accuracy_anova)
```
